Probing the Deuteron at Very Large Internal Momenta

### 2020-11-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/MARKED/ms.tex
updated PRL

carried out at Jefferson Lab (JLab) \cite{PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501} and Brookhaven National Lab (BNL) \cite{PhysRevLett.97.162504}. In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions

>>>>

carried out at Jefferson Lab (JLab) \cite{Subedi1476, PhysRevLett.113.022501,PhysRevLett.122.172502, Schmidt_2020} and Brookhaven National Lab (BNL) \cite{PhysRevLett.97.162504}. In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions
